\section{Purpose}
This document representing the Requirement Analysis and Specification Document is addressed to every person and entity interested in the project.  \\
\\
The aim of this document is both to picture the world the product would live in, including high level information that could be useful for stakeholders, and to provide specific information for developers or any technical stuff interested in implementing the product. It was also prominent concern to give a correspondence between client desires (and necessities) and the editing of functional and non-functional requirements. \\
\\
In this document it has been took particularly regard toward the comprehensibility and accuracy in order to be accessible to every individual that could have a perspective for the project. 
\subsection{Goals}
\begin{itemize}
\item
[\textbf{G1}] Allow users to properly use the services they wish to employ
\item
[\textbf{G2}] Allow visitor to register as individual or third-party user
\item
[\textbf{G3}] Allow individual users to monitor their location and health parameters
\item
[\textbf{G4}] Allow third-party users to request the data on specific users
\item
[\textbf{G5}] Allow individual users to approve or deny the specific request for their data
\item
[\textbf{G6}] Allow third-party users to request data on anonymized groups of individual users
\item
[\textbf{G7}] Call an ambulance if the system detects a critical health condition
\item
[\textbf{G8}] Allow third-party users to organize running competitions
\item
[\textbf{G9}] Allow Individual users to enrol in existing running competitions as participants 
\item
[\textbf{G10}] Allow Individual users to subscribe in existing running competition as spectators to monitor underway competitions
\end{itemize}


%-------------------------------------------------------------------------------------------------------------
\section{Scope}
The service Data4Help is designed to monitor the location and health status of individual registered to it using wearable devices. Upon registration individual users agree to the acquisition and usage of data by TrackMe and will be able to do see their own data.
The collected data is available to be requested by registered third-party users. The first possibility is requesting data on a specific individual user, for which it is required an identification code of the individual user(Social security number, fiscal code, etc.); the second possibility is accessing anonymized data on groups of individual users, so the system will have to allow third-party users to filter the users by age, geographic area, weight, etc. while keeping the data properly anonymized.
For both possibilities third-party users can simply acquire the data stored or subscribe to receive the data as soon as it is produced.
\\
\\
AutomatedSOS is a service designed to provide emergency health support for elderly people, to be integrated on top of Data4Help. Those individual users’ parameters about blood pressure, heartbeat and blood oxygenation are constantly checked: whenever they represent a critical health condition, AutomatedSOS, within 5 seconds from the drop of those values, contacts an emergency service asking to send an ambulance at the user location.
\\
\\
The main purpose of the Track4Run is to support running competition organizer and jogging lovers in convening great sport events with little effort. Namely Track4Run is a service-to-be focused on organizing running competition and on monitoring competitors. A user of Track4Run will also have to be a user of Data4Help. 
\\ 
\\
Third-party users will be able to: 
\begin{itemize}
\item 
organize a running competition specifying time, path of the competition, restrictions on participants and message for who wants to enroll;
\item 
see the participants; 
\item 
cancel a run they have organized. 
\end{itemize}

Individual users will be able to: 
\begin{itemize}
\item 
discover new nearby runs upon their creation by an app notification; 
\item 
be notified if a run they are participants in is canceled; 
\item 
search for organized runs and register to participate in a future run or spectate an ongoing run.
\end{itemize}
During the run: 
\begin{itemize}
\item 
organizer, participants and spectators will be able to see the name and positions of the participants; 
\item 
the system must be able to distinguish between actual participants and individual users who registered to the run but are not competing, simply checking if their position is on the run path. 
\end{itemize}

%-------------------------------------------------------------------------------------------------------------
\section{Definitions}
\begin{itemize}
\item \textit{Visitor}:someone that has not registered in yet;
\item \textit{User}: a person, third-party or user, that has registered;
\item \textit{Individual User}: every registered person from whom the system collects data; 
\item \textit{Run Participant}: an individual who wants to take part in a run;
\item \textit{Run Spectator}: an individual user who wants to spectate a run;
\item \textit{Third-Party User}:every entity registered with the purpose to request data for external use;
\item \textit{Run Organizer}: third-party users that wants to organize a run;
\item \textit{Emergency Service}: external participant that receives and take charge of the request for an ambulance;
\item \textit{Identification code}: a unique code for individual users or third-party users which identify them; for individual users it can be the Social security number, fiscal code, etc.; for third-party users it can be also the VAT number.
\item \textit{Stored Data}: the data on a IU collected so far.
\item \textit{Data Request}: a request for data made from a TPU.
\item \textit{Stored Data Request}: a data request for stored data.
\item \textit{Subscription Request}: a request for subscribing to newly generated data.
\end{itemize}
\section{Acronyms}
\begin{itemize}
\item RASD: Requirement Analysis and Specification Document. 
\item API: Application Programming Interface
\item TPU: Third-party User
\item RO: Run Organizer 
\item	RS: Run Spectator 
\item	RP: Run Participant 
\item	ES: Emergency Service 
\item	ID: Identification code
\item	D4H: Data4Help
\item	ASOS: AutomatedSOS
\item	T4R: Track4Run
\end{itemize}

\section{Abbreviations}
\begin{itemize}
\item Gn: n-goal
\item Dn: n-Domain assumption
\item Rn: n-Requirement
\end{itemize}

%-------------------------------------------------------------------------------------------------------------
\section{Revision history}
\begin{itemize}
\item \textbf{v0.1 - 19/10/18} Added a partial version of the introduction section
\item \textbf{v0.2 - 26/10/18} Added the whole Overall description section
\item \textbf{v0.3 - 1/11/18} Added the specific requirements - external interface requirements section 
\item \textbf{v0.4 - 3/11/18} Added the specific requirements - functional requirements, performance requirements sections
\item \textbf{v0.5 - 8/11/18} Updated user interfaces section, added design constrains and software system attributes sections
\item \textbf{v1.0 - 10/11/18} Added the alloy and the effort sections, updated introduction section 
\item \textbf{v1.1 - 11/11/18} Minor changes
\end{itemize}
%-------------------------------------------------------------------------------------------------------------
\section{Document Structure}
\paragraph{\hyperref[sect:introduction]{Introduction}} In this first section the scope of the project and its goals are described in general tems and is introduced an outline of the system that ise examined in further detail in the others sections. Furthermore, recurring Acronyms, Definitions and Abbreviations used in the document are introduced to ease its understanding.
\paragraph{\hyperref[sect:overview]{Overview}} The second section provide a more precise overview of the shared phenomena, via the product perspective and the class diagram, while also describing the main function the system will have, defining it further. It contains also the assumpion made on the outside world, the contraints on the project and the dependency between Data4Help, AutmatedSos and Track4Run.
\paragraph{\hyperref[sect:requirements]{Specific Requirements}} The third section contains a visual rapresentation of the communication interface with the users and a description of the software and ardware interfaces. Morover the requirements are outlined in detail, via the use of scenarios and relative use cases and sequence diagram, and mapped on the goals. Furthermore the system attributes are introduced in detail.
\paragraph{\hyperref[sect:alloy]{Formal Analysis Using Alloy}} The fourth section, being D4H, ASOS and T4R fairly indipent, contains three alloy models, one for each, and the relative results and generated world.
\paragraph{\hyperref[sect:effort]{Effort Spent}} The fifth section contains the effort spent by each member of the group.
\paragraph{\hyperref[sect:references]{References}} Reference documents and software used for the making of the document


