\subsection{Purpose}
\subsubsection{Goals}
\begin{itemize}
\item
[\textbf{G1}] Monitor the location and health status of users 
\item
[\textbf{G2}] Third parties can request the saved data 
\item
[\textbf{G3}] Third parties can subscribe to the data to receive it as produced 
\item
[\textbf{G4}] Third parties can request data on specific users 
\item
[\textbf{G5}] The users can approve or deny the specific request for their data 
\item
[\textbf{G6}] Third parties can request data on groups on individuals 
\item
[\textbf{G7}] The data on groups must be properly anonymized 
\item
[\textbf{G8}] Call the ambulance if the system detects a critical health condition 
\item
[\textbf{G9}] Users can organize running competition 
\item
[\textbf{G10}] Organizators can monitor the enrols or cancel a comeptition. 
\item
[\textbf{G11}] Users can enrol in existing running competition as competitors
\end{itemize}


%-------------------------------------------------------------------------------------------------------------
\subsection{Scope}
The service Data4Help is designed to monitor the location and health status of individual registered to it using wearable devices. Upon registration the users agree to the acquisition and usage of data by TrackMe. 
The collected data is available to third parties to request after registering to Data4Help. The first possibility is requesting data on a specific individual, for which it is required an identification of the user; The second possibility is accessing anonymized data on groups of users, so the system will have to allow third parties to filter the users by age, geographic area, weight, etc. while keeping the data anonymized.
For both possibilities third parties can simply acquire the data stored or subscribe to receive the data as soon as it is produced.
AutomatedSOS is a service designed to provide emergency health support(?) for elderly people, to integrate on top of Data4Help. Those users’ parameters about blood pressure, heartbeat and blood oxygenation are constantly checked: whenever they represent a critical health condition, AutomatedSOS, within 5 seconds from the drop of those values, contacts an emergency service asking to send an ambulance at the user location.
The main purpose of the Track4Run is to support running competition organizer and jogging lovers in convening great sport events with little effort. Namely Track4Run is a service-to-be focused on organizing running competition and on monitoring competitors. A user of Track4Run will also have to be a user of Data4Help. 
\\ \\Users will be able to: 
\begin{itemize}
\item 
organize a running competition specifying time, path of the competition, restrictions on participants and message for who wants to enroll and, once organized, see the enrolled users; 
\item 
cancel a race they have organized and be notified if a race they are enrolled to is canceled; 
\item 
discover new nearby races upon their creation; 
\item 
search for organized races and register to compete in a future race or spectate an ongoing race.
\end{itemize}
During the race: 
\begin{itemize}
\item 
the competing and the spectating users will be able to see the name and positions of the participants; 
\item 
the system must be able to distinguish between actual participants and users who registered to the race but are not competing, simply checking if their position is on the race path.
\end{itemize}

%-------------------------------------------------------------------------------------------------------------
\subsection{Definitions, Acronyms, Abbreviations}
%-------------------------------------------------------------------------------------------------------------
\subsection{Revision history}
%-------------------------------------------------------------------------------------------------------------
\subsection{Reference Documents }
%-------------------------------------------------------------------------------------------------------------
\subsection{Document Structure}

